Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas

### 2021-04-14 analysis/paper/paper.Rmd
UPDATE EXPLANTORY COV TABLE

```{r tblCovariates, include=TRUE, tab.id = "tblCovariates", tab.cap = "Explanatory covariates used in analyses of binary haul-out records for ice-associated seals."}
covariate_tbl <- tibble::tribble(
  ~Covariate, ~Type, ~Source, ~Description,
  "Age-sex class",   "Categorical", "Field Assessment", 
  "Classes included young-of-the-year, subadult, adult male and adult female. Young-of-the-year tags surviving past 1 March of the next year were treated as subadult in subsequent years.",
  "Hour", "Continuous; Fourier basis", "Bio-logger", 
  "Local solar hour using 6 variables of a Fourier-series basis to allow circularity, flexibility, and dimension reduction ",
  "Day",   "Continuous", "Bio-logger", 
  "Linear, quadratic, and cubic effects of day-of-year were modeled",
  "Precip", "Continuous", "NARR", 
  "Convective precipitation (kg/m2)",
  "Pressure", "Continuous", "NARR", 
  "Atmospheric pressure at sea level (kPa)",
  "Temp", "Continuous", "NARR",
  "Air temperatures predicted at 2m above the earth’s surface",
  "Wind", "Continuous", "NARR", 
  "Northerly and easterly vector components for wind were downloaded and converted into a single wind speed via the Euclidean norm.",
  "Northing", "Continuous", "Bio-logger","For bearded seals a measurement of northing was caclulated as latitude divided by the mean latitude across all locations"
)

>>>>

```{r tblCovariates, include=TRUE, tab.id = "tblCovariates", tab.cap = "Explanatory covariates used in analyses of binary haul-out records for ice-associated seals."}
covariate_tbl <- tibble::tribble(
  ~Covariate, ~Type, ~Source, ~Description,
  "Age-sex class",   "Categorical", "Field Assessment", 
  "young-of-the-year, subadult, adult male and adult female",
  "Hour", "Continuous; Fourier basis", "Bio-logger", 
  "local solar hour using 6 variables of a Fourier-series basis",
  "Day",   "Continuous", "Bio-logger", 
  "linear, quadratic, and cubic effects of day-of-year",
  "Precip", "Continuous", "NARR", 
  "convective precipitation (kg/m2)",
  "Pressure", "Continuous", "NARR", 
  "atmospheric pressure at sea level (kPa)",
  "Temp", "Continuous", "NARR",
  "air temperatures at 2m above the earth’s surface",
  "Wind", "Continuous", "NARR", 
  "northerly and easterly vector components for wind converted into a single wind speed via the Euclidean norm",
  "Northing", "Continuous", "Bio-logger","latitude divided by the mean latitude across all locations (for bearded seals only)"
)
